Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2021-11-08 analysis/paper_draft2.Rmd
revised references, text spacing after equations
revised spacing

The posterior distribution does not have a closed form.  Accordingly, we used the Metropolis-Hasting algorithm to sample $b$ from the posterior distribution. To measure convergence, we used trace plots, the Gelman-Rubin convergence diagnostic and Geweke’s diagnostics [@Gelman1992; @Gelman1998;@Geweke1992].

@@

To illustrate, suppose the strike tally in Table 1 depicts the pattern of strikes in the present case with a prosecuting attorney Aaron Waelchi and defense attorney Lawrance Klocko V (both aliases for actual attorneys in the historical strike data). After the user enters this strike tally, the app initially displays two graphs -- one for the prosecution and the defense. Each graph depicts the prior density plot (colored grey) and posterior density plot (blue and red for defense and prosecution, respectively) for the bias parameter (Figure 5).

>>>>

The posterior distribution does not have a closed form.  Accordingly, we used the Metropolis-Hasting algorithm to sample $b$ from the posterior distribution. To measure convergence, we used trace plots, the Gelman-Rubin convergence diagnostic and Geweke’s diagnostics [@Gelman1992;@Gelman1998;@Geweke1992].

@@

To illustrate, suppose the strike tally in Table 1 depicts the pattern of strikes in the present case with a prosecuting attorney Aaron Waelchi and defense attorney Lawrance Klocko V (both aliases for actual attorneys in the historical strike data). After the user enters this strike tally, the app initially displays two graphs -- one for the prosecution and the defense. Each graph depicts the prior density plot (colored light grey) and posterior density plot (blue and red for defense and prosecution, respectively) for the bias parameter (Figure 5).
